timesliced_random_cell_selection

### 2018-10-29 src/timesliced_random_cell_selection.Rmd
progress with loop to find all unoccupied cells in each timeslice (missing correct .csv naming)

ok so now I have a base list to work off... I have split the cells with presence data into a list by time-slice (split_obs_cell_yymm) (code in biological_data_prep)

```{r}
test_timeslice <- split_obs_cell_yymm[1]
test_timeslice <- as.data.frame(test_timeslice)
test_time_cell <- unique_cell_centroid
test_time_cell <- test_time_cell[!test_time_cell$cell_id %in% test_timeslice$X1998.10.cell_id, , drop = FALSE]
```
ok that works... but you need to pop into a loop and dynamically name the output (and create a .csv maybe)

```{r}

>>>>

ok so now I have a base list to work off...

Split the data_aea into timeslices (year/month).
All you need is the year, month, cell_id
```{r}
cell_yymm <- subset(data_aea, select= c(cell_id, year, month)) #create a new df with just cell_id, yr, month
split_cell_yymm <- split(cell_yymm, list(cell_yymm$year, cell_yymm$month), drop = TRUE)
```

What I want to do is for each time slice, create a list of all cells, then remove the ones where observations occured

```{r}
test_timeslice <- split_cell_yymm[[1]]
test_timeslice
test_timeslice <- as.data.frame(test_timeslice)

timeslice_name <- name(split_cell_yymm(1))
test_time_cell <- unique_cell_centroid
test_time_cell <- test_time_cell[!test_time_cell$cell_id %in% test_timeslice$cell_id, , drop = FALSE]
write.csv(test_time_cell, "../output/bio/test_time_cell.csv", row.names = FALSE)
```
ok that works... but you need to pop into a loop and dynamically name the output (and create a .csv maybe)

need a loop to create a copy of the unique_cell_centroid dataframe, and give it the same name as the splitobs_cell_yymm level

this almost works - just need it to assign a name not a list number. note the output goes to /src....
```{r}
no_timeslices <- length(split_cell_yymm) # how many levels (time slices) are in the list
for (i in 1:no_timeslices){
  test_timeslice <- split_cell_yymm[[i]]
  test_timeslice <- as.data.frame(test_timeslice)
  test_time_cell <- unique_cell_centroid
  test_time_cell <- test_time_cell[!test_time_cell$cell_id %in% test_timeslice$cell_id, , drop = FALSE]
  write.csv(test_time_cell, paste0(i, ".csv"), row.names = FALSE)
}
